Standard Candle Cosmology With Incomplete Spectroscopic Classification

### 2015-11-05 doc/article.tex
more train of thought

The probability for the data to be in a specific configuration $b_k$ of
being below or above flux threshold is expressed
as
\begin{equation}
p(data, b_k| model)  = \epsilon(Photometry_o, b_k)p(data| model)\\
\end{equation}
where
\begin{equation}
\epsilon(Photometry_o; b_{k})= \prod_{\nu i}\mathcal{H}\left((-1)^{b_{k\nu i}+1}(Photometry_{o,k\nu i}-Threshold_{\nu i})\right),
\end{equation}
where $\mathcal{H}$ is the Heaviside step function; when $b_{k\nu i}=1/0$ the step in the efficiency
is up/down.  The indices correspond to configuration $k$,
transient $\nu$, and photometric point $i$.

@@

A clean deliverable would be:
\begin{itemize}
\item Determination of flux thresholds for each photometric point given
a $S/N$ threshold
\begin{equation}
threshold(point, S/N).
\end{equation}
If we work in the sky-noise dominated regime, I believe this information is already
calculated by DM.
\end{itemize}

@@

@@

\begin{itemize}
\item Calibration model and uncertainties. Assuming we work with zeropoints
$p(Z)$ is needed.
\item Data! Spectroscopic Type and uncertainties, Spectroscopic redshifts and
uncertainties, galaxy properties and uncertainties, host-galaxy associations
and uncertainties, photometry and uncertainties.
\item Determine the mechanics of doing the analysis.  A Bayesian MCMC could produce posteriors, which sampler that best suits our needs? Is a frequentist
analysis technically unfeasible? If redshifts were free to wander I would think so, but maybe
it is possible in this model.
\end{itemize}

>>>>

The probability for the data to be in a specific configuration $b_k$ of
being below or above flux threshold is expressed
as
\begin{equation}
p(data, b_k| model)  = \epsilon(Photometry_o, b_k)p(data| model)\\
\end{equation}
where
\begin{equation}
\epsilon(Photometry_o; b_{k})= \prod_{\nu i}\mathcal{H}\left((-1)^{b_{k\nu i}+1}(Photometry_{o,k\nu i}-Threshold_{\nu i})\right),
\label{eff:eqn}
\end{equation}
where $\mathcal{H}$ is the Heaviside step function; when $b_{k\nu i}=1/0$ the step in the efficiency
is up/down.  The indices correspond to configuration $k$,
transient $\nu$, and photometric point $i$.

@@

\subsection{Detection Criteria (Malmquist Bias)}
The photometric selection criteria are expected to be significantly more rigorous that
the detection criteria.  Nevertheless, the detection efficiencies need to be characterized.
Fakes already provide a good measure of this.  To first order, the efficiency depends
on $S/N$, but a secondary dependence on the structure of background galaxies.
The detection efficiency is more complicated than the step function
shown in Eqn.~\ref{eff:eqn}.

Deliverable is the detection efficiency to take the place of Eqn.~\ref{eff:eqn}.

\subsection{Per-Exposure Thresholds}
To understand the effect of sample-selection criteria and detection efficiency
on a specific object, the
properties of each photometric point is needed.  Although the photometric criteria
have not been formalized, a $S/N$ threshold is a possible statistic to be used.
As such, a clean deliverable would be:
\begin{itemize}
\item Determination of flux thresholds for each photometric point of each candidate
given
a $S/N$
\begin{equation}
threshold(point, S/N).
\end{equation}
If we work in the sky-noise dominated regime, I believe this information is already
calculated by DM.
\end{itemize}

@@

\subsection{Photometric Data}

Deliverable:
transient counts and associated covariance matrix.  For flexibility, the counts and the
flux calibration are delivered separately.

\subsection{Calibration model and uncertainties}
For the first analysis, it is presumably sufficient to describe calibration uncertainties
as global zeropoints.  In the long term, it would be great to have a transmission
function for every photometric point.

It has to be decided whether calibration should be included
as part of the photometric uncertainties, or as model parameters.
The former requires the inversion of a full covariance matrix for all photometric
points.  The latter may have a per-SN solution through importance sampling.

Deliverable of $p(Z)$.

@@

\begin{itemize}
\item Data! Spectroscopic Type and uncertainties, Spectroscopic redshifts and
uncertainties, galaxy properties and uncertainties, host-galaxy associations
and uncertainties, photometry and uncertainties.
\item Determine the mechanics of doing the analysis.  A Bayesian MCMC could produce posteriors, which sampler that best suits our needs? Is a frequentist
analysis technically unfeasible? If redshifts were free to wander I would think so, but maybe
it is possible in this model.
\end{itemize}
